---
title: "Satellites"
author: "Frederic TWAHIRWA"
date: "11 février 2017"
output: html_document
---

```{r}

rm(list=ls(all=TRUE))

```

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(data.table)
library(ggplot2)
library(rworldmap)
library(ggmap)
library(geosphere)
library(RColorBrewer) 
library(forecast)
```
Data cleaning 
The data set required some transformations. 
- rename columns 
- remove strings in numerical columns 
- mutate news columns to keep informations removed in numerical culumns such as "end of life"" or "biginning of life""
- NR country as country of UN registry is replaced by the country owner name
- There are two data set sattellites and satdata will be loaded 


```{r}
satellites<-fread(file='satellites.csv')
satdata<-fread(file='satdata.csv')
str (satellites)
#geo <- geocode((satellites$country_of_UN_registry))

satContryOwner <- satellites %>% 
        group_by(country_of_owner) %>% 
        summarise (number = n())

# usa -> "USA"
# eu > "Belgium" , " Denmark"

```

Exploring data 
 - recency : based on the dataset 438 satellites exceed their expected life time
 - activitities by days and months :  the finding is that there are far few satellites launched in January while the peack of activity lies on Thusday  (by day) and in June (by month)
 _ The major parrty of satellites are launched in  second half-year

```{r}

# add a new column to highliht the satellite recency  and verify if there are satellites which ecxeeds their expected life delay 
# 438 sateliites exceed their expeted life delay
satellites$years_since <- as.numeric(2017- satellites$year_of_launch) 
satellites$exceed_expected_life <-as.numeric (satellites$years_since > satellites$expected_lifetime)
n_sat_exceed_expected_life <- sum (satellites$exceed_expected_life, na.rm=TRUE)

#replace NR by noum of owner country
satellites$country_of_UN_registry[which(satellites$country_of_UN_registry=="NR")]<-
        satellites$country_of_owner[satellites$country_of_UN_registry=="NR"]

theme1 <- theme (plot.title = element_text(color="blue", size=14, hjust =0.5, face="bold.italic"),
             axis.title.x = element_text(color="blue", size=12, face="bold"),
             axis.title.y = element_text(color="blue", size=12, face="bold"))

ggplot(satellites, aes(weekday_of_launch, fill=factor(month_of_launch))) +
        geom_bar() + 
        ggtitle( "satellites launched by weekday and month") +
        labs(x="The weekday of launch", y="Number of satellites") + 
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5)) +
        theme1

ggplot(satellites, aes(x = factor(month_of_launch))) +
        geom_bar(fill="skyblue") + 
        ggtitle( "satellites launched by  month") +
        labs(x="launch Month", y="Number of satellites") + 
        theme1

ggplot(satellites, aes(weekday_of_launch, fill=factor(month_of_launch))) +
        geom_bar(position="dodge") +
        ggtitle( "satellites launched by weekday and month") +
        labs(x ="Country of UN registry",y ="Number of satellites") +
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5)) +
        theme1

ggplot(satellites, aes(x = factor(month_of_launch), fill=factor(weekday_of_launch))) + 
        geom_bar(position="dodge") + 
        ggtitle( "satellites launched by weekday") +
        labs(x ="Launch Month", y ="Number of satellites") +
        theme1


number_by_wday_of_launch<-satellites %>% 
        group_by(weekday_of_launch) %>% 
        summarise(number_by_weekday=n()) %>% 
        arrange(desc(number_by_weekday))

number_by_month_of_launch<-satellites %>% 
        group_by(month_of_launch) %>% 
        summarise(number_by_month=n()) %>% 
        arrange(desc(number_by_month))

number_by_year_of_launch<-satellites %>% 
        group_by(year_of_launch) %>% 
        summarise(number_by_year=n()) %>% 
        arrange(desc(year_of_launch))

ggplot(number_by_year_of_launch, aes(x=year_of_launch, y=number_by_year,
                                     size=number_by_year, col=number_by_year))+
        geom_point(alpha=0.8)+
        geom_smooth(se=F, linetype = 2)+
        ggtitle( "actives satellites in orbit up to 2016") + 
        labs( x="launch year", y="Number launched by year") +
        theme1
        

ggplot(satellites, aes(x=1, y=perigee, col=factor(class_of_orbit))) +
        geom_point(alpha=.5, position=position_jitter(width=1)) 

```

EXPLORING DATA SEGMENTATION 
 - number of active satellites by country

 
 Comments : 
 - 38.4% of satellites are under the sole USA Flag
 - Chine is in second position, and trying to catch up in the area of satellites in orbit
 - 7 countries have at least 40 actives satellites on orbit
 - 23 satellites are at least under the flg of two countries

```{r}
origin_country<- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        arrange(desc(sat_number_from_orig_country)) %>% 
        mutate (percent=round(100*sat_number_from_orig_country / sum (sat_number_from_orig_country),1))

share_sat<- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        filter(grepl("/", country_of_UN_registry)) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        arrange(desc(sat_number_from_orig_country)) %>% 
        mutate (percent=round(100*sat_number_from_orig_country / sum (sat_number_from_orig_country),1))

n_of_shared_sat <- sum (share_sat$sat_number_from_orig_country)

# countries that have few satellites in orbit less than 40 
country_low_power <- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        filter (sat_number_from_orig_country < 40) %>%  # the threshold is set @ 40 satellites 
        arrange(desc(sat_number_from_orig_country))

n_low_power_countries <- sum (country_low_power$sat_number_from_orig_country)

# countries that have more 40 satellites in orbit 
country_high_power <- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        filter (sat_number_from_orig_country >= 40) %>% 
        arrange(-sat_number_from_orig_country) %>% 
        rbind (c("Others countries ", n_low_power_countries))


# visualizing the share umbalance and the USA power
share_sat_plot <- ggplot(country_high_power,
                         aes(x=reorder(country_of_UN_registry, -as.numeric(sat_number_from_orig_country)),
                                                 y = as.numeric(sat_number_from_orig_country))) +                          geom_bar(stat="identity", fill="steelblue") + 
      
        geom_text(aes(label=sat_number_from_orig_country), vjust=1.5, color="white", size=4) + 
        ggtitle( "Satellites distribution by county") + 
        scale_fill_discrete(name="countries :")+
        scale_x_discrete(name ="Country of UN registry") +  # rename x axis
        scale_y_discrete(name ="Number of satellites") + # rename y axis
        theme_minimal() 
share_sat_plot


US_vs_chine <- satellites %>% 
        group_by(country_of_UN_registry, year_of_launch) %>% 
        filter((country_of_UN_registry=="USA" | country_of_UN_registry=="China" |
                        country_of_UN_registry=="France") & (year_of_launch < 2016 & year_of_launch > 1996)) %>%
        summarise(sat_number_from_orig_country=n()) %>% 
        arrange(desc(year_of_launch))

# visualizing USA power compared to China and France on the past years 
ggplot(US_vs_chine, aes(x=year_of_launch, y=sat_number_from_orig_country,
                        group = country_of_UN_registry, colour = country_of_UN_registry)) +
        
        
        geom_line() +
        scale_fill_discrete(name="countries :")+
        geom_point( size=4, shape=21, fill="white")
      

# visualizing USA power compared to China and France on the past years  with bar plot
ggplot(US_vs_chine, aes(x=year_of_launch, y=sat_number_from_orig_country,
                        fill=factor(country_of_UN_registry))) +
        scale_fill_discrete(name="countries :")+
        geom_bar(stat = "identity", position="dodge")


# The world distribution 
# the world map
names(origin_country)<- c("region", "sat_number_from_orig_country")
all_states <- map_data("world")
world_sat <-inner_join(all_states, origin_country, by="region")

#plot all states with ggplot

world_base <- ggplot(data = all_states, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.5) + 
  geom_polygon(color = "white", fill = "gray")


World_n_sat<-world_base +
        geom_polygon(data = world_sat, aes(fill = sat_number_from_orig_country), color = "white")+
        #scale_fill_continuous(name = "number satellite per Country")+ 
        scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(10, 50, 100, 200, 300, 400),
                         trans = "log10")+
        ggtitle( "Satellites distribution by county at golbal level")
        theme_bw()
       
World_n_sat
```

EXPLORING DATA SEGMENTATION 
 - number of active satellites by launch site
 - more satellites were launched from "Baikonur Cosmodrome"
 
 Findings : 
 - 38.4% of satellites are under the sole USA Flag
 - Chine is in second position
 - 7 countries have at least 40 actives satellites on orbit
 - 23 satellites are at least under the flg of two countries


```{r}
site_of_launch <-satellites %>% 
        group_by (launch_site) %>%
        summarise(sat_number_by_site=n(), total_mass= sum(launch_mass, na.rm=TRUE),
                  min_mass= min (launch_mass, na.rm=TRUE),
                  max_mass = max (launch_mass, na.rm=TRUE), mean_mass = mean(launch_mass, na.rm=TRUE),
                  sd_mass = sd(launch_mass, na.rm = TRUE))  %>%
        top_n(10, sat_number_by_site) %>% 
        arrange (desc (sat_number_by_site)) %>% 
        mutate(percentage = round(100*sat_number_by_site / sum(sat_number_by_site),1)) %>% 
        mutate(pos=cumsum(sat_number_by_site)-sat_number_by_site /2)

# visualizing where satellites are launched by site        
bp_site = ggplot(site_of_launch, aes(x= reorder(launch_site, -as.numeric(sat_number_by_site)),
                                     y = sat_number_by_site, fill = factor(launch_site)))+
        geom_bar(stat="identity") +  #??? aggregate data into accounts 
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5)) + # vertical label
        geom_text(aes(label=sat_number_by_site), vjust=1.5, color="white", size=4) + 
        ggtitle( "Where active satellites are launched") + 
        scale_x_discrete(name ="Site") + 
        scale_y_discrete(name ="Number of satellites") 
bp_site

bp_site_mass = ggplot(site_of_launch, aes(x= reorder(launch_site, as.numeric(total_mass)),
                                     y = total_mass, fill = factor(launch_site)))+
        geom_bar(stat="identity") + 
        coord_flip() +
        geom_text(aes(label=total_mass), vjust=-4.0, color="black", size=3) + 
        ggtitle( "total mass in orbit by site ") + 
        scale_fill_discrete(name="Launch site")+
        scale_x_discrete(name ="Site") + 
        scale_y_discrete(name ="Mass total") 
bp_site_mass

veh_of_launch <-satellites %>% 
        group_by (launch_site, launch_vehicule) %>% 
        summarize (sat_by_veh= n()) %>% 
        arrange (desc (sat_by_veh))
```

- Exploring data 
 - display number of satellites given their expected life and highlight their distribution based on their users and class of orbit
 - This information can help in dealing with missing value
 - 39 % of actives satellites : Commercials
 - 20 % of actives satellites : governments
 - 39 % of actives satellites : Military
 - 49 % 
Distribution by class 
 - Since the 2000s, the number of Elliptical, MEO and GEO satellites launched haven't changed while the number of LEO have significantly increased from 35 in 2010 to 119 in 2015
 

```{r}

# visualization of satellites expected liftime by sector
ggplot(satellites, aes(x=expected_lifetime, fill=users)) +
        geom_histogram(binwidth=1, alpha=.5, position="identity")+
        ggtitle( "distribution: Satellites expected lifetime by sector") + 
        labs( x="expected lifetime", y="satellites number") +
        theme1

# visualization of satellites by class of orbit
ggplot(satellites, aes(x=expected_lifetime, fill=class_of_orbit)) + 
        geom_histogram(binwidth=1, alpha=.5, position="identity") +
        ggtitle( "distribution : Satellites by class of orbit") + 
        labs( x="expected lifetime", y="satellites number") +
        theme1

# distribution of satellites in orbit  by sector and purpose
sat_users <- satellites %>% 
        group_by (users) %>%
        summarise (sat_number_by_users=n(), min_exepect_life = round(min (expected_lifetime, na.rm=TRUE),1),
                  max_expect_life = round(max (expected_lifetime, na.rm=TRUE),1),
                  mean_expect_life = round(mean(expected_lifetime, na.rm=TRUE),1),
                  sd_expect_life = round(sd(expected_lifetime, na.rm = TRUE),1))  %>%
        mutate (percent=round(100*sat_number_by_users / sum (sat_number_by_users),0)) %>% 
        arrange (desc (sat_number_by_users))

sat_purpose <- satellites %>% 
        group_by (purpose) %>%
        summarise (sat_number_by_purpose=n())  %>%
        mutate (percent = round(100*sat_number_by_purpose / sum (sat_number_by_purpose),0)) %>% 
        arrange (desc (sat_number_by_purpose))

sat_users1 <- satellites %>% 
        group_by (users, purpose) %>% 
        summarise (sat_number_by_userp = n()) %>%
        arrange (desc (sat_number_by_userp)) 
        #mutate (percent = round(100*sat_number_by_userp / sum (sat_number_by_userp),0))

        

sat_class <- satellites %>% 
        group_by (class_of_orbit) %>%
        summarise (number_by_class=n(), min_exepect_life = round(min (expected_lifetime, na.rm=TRUE),1),
                  max_expect_life = round(max (expected_lifetime, na.rm=TRUE),1),
                  mean_expect_life = round(mean(expected_lifetime, na.rm=TRUE),1),
                  sd_expect_life = round(sd(expected_lifetime, na.rm = TRUE),1))  %>%
        mutate (percent = round (100*number_by_class / sum (number_by_class) )) %>% 
        arrange (desc (number_by_class))

# visualization of satellites by class of orbit
ggplot(sat_class, aes(x=class_of_orbit, y=number_by_class, fill=factor(class_of_orbit))) + 
        geom_bar(stat = "identity", position="dodge") + 
        ggtitle( "Satellites number  by class of orbit") + 
        labs( x="class of orbit", y="satellites number") +
        theme1

sat_class_ts <- satellites %>% 
        group_by (class_of_orbit, year_of_launch) %>%
        filter (!is.na(class_of_orbit) & year_of_launch < 2016 & year_of_launch > 1998) %>% 
        summarise (number_by_class=n())  %>%
        mutate (percent = round (100*number_by_class / sum (number_by_class) )) %>% 
        arrange (desc (year_of_launch))

# visualization of satellites by class of orbit and year of launch
ggplot(sat_class_ts, aes(x=year_of_launch, y=number_by_class, fill=factor(class_of_orbit))) + 
        geom_bar(stat = "identity", position="dodge") + 
        ggtitle( "Satellites number by launch year and class of orbit") + 
        labs( x="launch year", y="sat number by class of orbit") +
        theme1

ggplot(sat_class_ts, aes(x=year_of_launch, y=number_by_class,
                        group = class_of_orbit, colour = class_of_orbit)) + 
        geom_line(size=1.5) + 
        geom_point( size=4, shape=21, fill="white")+
        ggtitle( "Satellites number by launch year and class of orbit") + 
        labs( x="launch year", y="sat number by class of orbit") +
        theme1

```


Owner and purpose

```{r}
sat_Owner<- satellites %>% 
        group_by (owner, country_of_owner) %>% 
        summarise (number_by_owner=n())  %>% 
        arrange (desc (number_by_owner))

sat_Owner_purpose <- satellites %>% 
        group_by (owner,country_of_owner, users) %>% 
        summarise (number_by_owner_purpose=n())  %>% 
        arrange (desc (number_by_owner_purpose))


```



```{r}


linreg_ls <- lm (launch_site ~ purpose + class_of_orbit, data = satellites)
summary(linreg_ls)

pred1 <- predict(linreg_ls, type="response")
pred1
table (satellites$launch_site, pred1 >= 0.5)


```

```{r}
# cov (sat_expected_life$expected_lifetime,sat_expected_life$users)

```



Time series
- try to forecast number of satellites launched in 2016 given satellites (actives) in orbit launched in 11 previous years
- 

```{r}

sat_by_year <- satellites %>% 
        group_by(year_of_launch) %>% 
        filter ( year_of_launch>=2005 & year_of_launch < 2016) %>% 
        summarise (n_by_month=n())



timeseries_sat <- ts (sat_by_year[,2], start=2005, end=2015)
ts.plot (timeseries_sat)

#autocolrrelation 
acf(timeseries_sat, plot=FALSE) # acf [1]= 0.653 acf [2]= 0.351
n_sat_change <- diff (timeseries_sat)

#autoreggressive 
AR_sat<- arima (timeseries_sat, order=c(1,0,0)) 
print (AR_sat) # slope :1 , intercept: 252.3669, variance : 278.8

AR_sat_change <- arima (n_sat_change, order=c(1,0,0))

ts.plot(timeseries_sat)
AR_sat_fitted <- timeseries_sat- residuals(AR_sat)
points(AR_sat_fitted, type = "l", col = 2, lty = 2)

predict_AR_sat <-predict(AR_sat_fitted, 1) # 149

# Moving average
n_sat_change <- diff (timeseries_sat)

ts.plot(n_sat_change)
MA_sat_change <-arima (n_sat_change, order=c(0,0,1)) # slope =0.8349 , intercept=90.88, variance : 771
MA_sat_change_fitted <- n_sat_change - residuals(MA_sat_change)

points(MA_sat_change_fitted, type = "l", col = 2, lty = 2)
predict_MA_sat <-predict(MA_sat_change, 1)
print (predict_MA_sat)

MA_sat <-arima (timeseries_sat, order=c(0,0,1)) # slope =0.8349 , intercept=90.88, variance : 771
ts.plot(timeseries_sat)
MA_sat_fitted <- timeseries_sat - residuals(MA_sat)
points(MA_sat_fitted, type = "l", col = 2, lty = 2)

predict_MA_sat1 <-predict(MA_sat_fitted, 1) #110.9
print (predict_MA_sat1)

# comparison between AR and MA

AIC(AR_sat_change) # 81.98
AIC(MA_sat_change) # 82.04

BIC(AR_sat_change) # 82.89
BIC(MA_sat_change) # 82.95
##########################################################

auto_a_sat <- auto.arima(timeseries_sat)
auto_a_sat

```



Time series
- try to forecast number of satellites launched in 2016 given satellites (actives) in orbit launched in 5 previous years


```{r}
sat_by_year <- satellites %>% 
        group_by(year_of_launch) %>% 
        filter ( year_of_launch>=2010 & year_of_launch < 2016) %>% 
        summarise (n_by_year=n())

timeseries_sat <- ts (sat_by_year[,2], start=2010, end=2015)
plot(timeseries_sat)

#autocolrrelation 
acf(timeseries_sat, plot=FALSE) # acf [1]= 0.491 acf [2]= 0.055
n_sat_change <- diff (timeseries_sat)

#autoreggressive 
AR_sat<- arima (timeseries_sat, order=c(1,0,0)) 
print (AR_sat) # slope : 0.846 , intercept: 121.023, variance : 517.2

AR_sat_change <- arima (n_sat_change, order=c(1,0,0))

ts.plot(timeseries_sat)
AR_sat_fitted <- timeseries_sat- residuals(AR_sat)
points(AR_sat_fitted, type = "l", col = 2, lty = 2)

predict_AR_sat <-predict(AR_sat_fitted, 1) # 145.5

# Moving average
n_sat_change <- diff (timeseries_sat)

ts.plot(n_sat_change)
MA_sat_change <-arima (n_sat_change, order=c(0,0,1)) # slope =-0.9998 , intercept=20.14, variance : 91.45
MA_sat_change_fitted <- n_sat_change - residuals(MA_sat_change)

points(MA_sat_change_fitted, type = "l", col = 2, lty = 2)
predict_MA_sat <-predict(MA_sat_change, 1)
print (predict_MA_sat) #13.99 

MA_sat <-arima (timeseries_sat, order=c(0,0,1)) # slope =0.68 , intercept= 117.9, variance : 747
ts.plot(timeseries_sat)
MA_sat_fitted <- timeseries_sat - residuals(MA_sat)
points(MA_sat_fitted, type = "l", col = 2, lty = 2)

predict_MA_sat1 <-predict(MA_sat_fitted, 1) #113.58
print (predict_MA_sat1)

# comparison between AR and MA

AIC(AR_sat_change) # 45.07
AIC(MA_sat_change) # 44.55

BIC(AR_sat_change) # 43.09
BIC(MA_sat_change) # 82.38

# using auto.arim model 

```

```{r}
sat_by_month <- satellites %>% 
        group_by(year_of_launch, month_of_launch) %>% 
        filter ( year_of_launch>=2005 & year_of_launch < 2016) %>% 
        summarise (n_by_month=n()) %>% 
        arrange (year_of_launch)

# Here we can realize that some months lacking , so to I complete the data.frame by adding those months with zero as value of number of sat
# this help on computing time series anaysis 

y<- c(2006, 2009)
m <- c(1,3)
v <- c(0,0)
addrows<- data.table("year_of_launch"=y, "month_of_launch"=m,"n_by_month"=v)

sat_by_month <- rbind(as.data.frame(sat_by_month), as.data.frame(addrows))
sat_by_month <-arrange (sat_by_month,year_of_launch, month_of_launch)

#ts_sat <- ts (sat_by_month[,3], start=c(2005, 1), end=2015, frequency = 12)
ts_sat <- ts (sat_by_month[,3] + c(1:nrow(sat_by_month) %% 12 == 5) * 10, 
              start=c(2005, 1), end=2015, frequency = 12)


ts_sat
plot (ts_sat)

auto_a_sat <- auto.arima(ts_sat)
auto_a_sat

theforecast <-forecast(object=auto_a_sat, h = 12)
summary(theforecast)
plot (theforecast) 

## â•â•â•â•â•â•â•â•â•â•â•â•â•â•
## the resultf of the forecasting, how to intrepret them 
## There is a simple way to plot the forecast graph with ggplot ?
## â•â•â•â•â•â•â•â•â•â•â•â•â•â•

```
 
 
 - No Russian satellite have ever been launched from: Cape Canaveral, Vandenberg AFB, Guiana Space Center or Xichang Satellite Launch Center
 - At Cape Canaveral and Vandenberg AFB:  almost exlusivily USA satellites 
 
 
```{r}
satp <- satdata %>% 
        group_by(purpose, users) %>% 
        summarise(number = n()) %>% 
        arrange(-number)

ggplot(satp, aes(x=users,y=purpose,size=number)) +
        geom_point() +
        theme(axis.text.x = element_text(angle=90,hjust=1),
              axis.text=element_text(size=6),
              axis.title.y=element_blank(),axis.title.x=element_blank())

ggplot(satdata, aes(x=class_of_orbit, y=Guiana, col=factor(class_of_orbit))) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

ggplot(satdata, aes(x=class_of_orbit, y=Baikonur, col=factor(class_of_orbit))) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

ggplot(satdata, aes(x=class_of_orbit, y=Cape, col=factor(class_of_orbit))) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

ggplot(satdata, aes(x=class_of_orbit, y=Vandenberg, col=factor(class_of_orbit))) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

ggplot(satdata, aes(x=class_of_orbit, y=Xichang, col=factor(class_of_orbit))) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

######################################################
ggplot(satdata, aes(x=country_of_contractor, y=Guiana)) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

ggplot(satdata, aes(x=country_of_contractor, y=Baikonur)) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

ggplot(satdata, aes(x=country_of_contractor, y=Cape)) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))


ggplot(satdata, aes(x=country_of_contractor, y=Vandenberg)) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

ggplot(satdata, aes(x=country_of_contractor, y=Xichang)) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))

###################################################################

ggplot(satdata, aes(x=country_of_contractor, y= Cape)) +
        geom_point(alpha=.5, position=position_jitter(width=0.2))+
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))
```

Predctive analysis 
 - The expected life time of a satellite is highly related ( 90.5 percent ) to its purpose , class of orbit, power and the launch vehicle
 - The choice of the launch site is linked to the country of the contractor
    

```{r}
sat_expected_life <- satellites %>% 
        filter (!is.na(expected_lifetime))

ggplot(sat_expected_life, aes(x=expected_lifetime)) + 
        geom_histogram(aes(y=..density..),  color="black", fill="white")+ 
        geom_density(alpha=.2, fill="#FF6666") 

linreg_users=lm(expected_lifetime ~ purpose + class_of_orbit ,
                data=sat_expected_life)
par (mflow = c(2, 2))
plot(linreg_users)
summary(linreg_users)

# observations 462, 568, 882 appear to ber influential, then dropping those observations 
#... a better model fit

linregEL=lm(expected_lifetime ~ purpose + class_of_orbit + launch_mass + power+ launch_vehicule ,
                data=sat_expected_life[-c(462, 568, 882),])
summary(linregEL)

anova(linregEL)

# with this model LinregEL the fit has improved at 90.5% , then we can reject the null hypothesis, in addition 
# the p value of the F test is very small (< 2.2e-16).
# the anova () function - analysis of variance indicates that all variables (purpose, class_of_orbit,launch_mass, power, launch_vehicule) contribute to the reduction of the fitting error of the model

############################################################################???
############## Visual Diagnostics ###########################

fortdata <- fortify(linregEL)

## Homoscedacity assumption 

ggplot(data = fortdata, aes(x = .fitted, y = .resid)) + 
        geom_hline(yintercept = 0, colour = "firebrick3") +
        geom_point()+
        ggtitle( "Residual vs Fitted")

## Linearity assumption 

ggplot(data = fortdata, aes(x = .fitted, y = .resid)) + 
        geom_hline(yintercept = 0, colour = "firebrick3") + 
        geom_point() +
        geom_smooth(se = T) +
        ggtitle( " Linearity")

## Normality assumption 

ggplot(data = fortdata, aes(sample = .stdresid)) + 
        stat_qq() + 
        geom_abline(colour = "firebrick3")+
        ggtitle( "Normal Q-Q")

## Standardized residuals vs fitted values

ggplot(data = fortdata, aes(x = .fitted, y = .stdresid)) + 
        geom_hline(yintercept = 0, colour = "firebrick3") + 
        geom_point() + 
        ggtitle( "Scale-location")


## Residuals vs. leverages

ggplot(data = fortdata, aes(x = .hat, y = .stdresid)) + 
        geom_point() + 
        geom_smooth(se = FALSE)+
        ggtitle( "Residual vs Leverage")


```
```{r}

library (caTools)
library (rpart)
library (rpart.plot)
library (ROCR)

satpred<-fread(file='satpred.csv')
satpred <- satpred[,-c(1)]
table(satpred$Guiana)

set.seed (123)
splG<- sample.split (satpred$Guiana , SplitRatio = 0.7)
trainG <- subset (satpred, splG == TRUE)
trainG <- trainG[, -c(5:8)]
testG<- subset (satpred, splG == FALSE)
trainG <- trainG[, -c(5:8)]

GuianaCART <- rpart(Guiana ~ ., data=trainG, method= "class")
prp (GuianaCART)

printcp(GuianaCART)
plotcp(GuianaCART )

predG <- predict (GuianaCART, newdata = testG)
pred.probG <- predG[,2]
table(testG$Guiana, pred.probG >=0.32)

accurracyGuiana <- (248+62)/(248+64+5+62) # 81.8 percent
#predictCARTG <- predict (GuianaCART, newdata=testG, type="class")
#table(testG$Guiana, predictCARTG)

predGROCR <- prediction(pred.probG, testG$Guiana)
perfGROCR <- performance(predGROCR, "tpr", "fpr")
plot(perfGROCR, colorize=TRUE)
####################################_

set.seed (123)
splB<- sample.split (satpred$Baikonur , SplitRatio = 0.7)
trainB <- subset (satpred, splB == TRUE)
testB<- subset (satpred, splB == FALSE)

BaikonurCART <- rpart(Baikonur ~ ., data=trainB[, -c(4, 6:8)], method= "class")
prp (BaikonurCART)
printcp(BaikonurCART)
plotcp(BaikonurCART)


predB <- predict (BaikonurCART, newdata = testB)
pred.probB <- predB[,2]
table(testB$Baikonur, pred.probB >=0.2)

######################################
################Cape ###################
set.seed (123)
splC<- sample.split (satpred$Cape , SplitRatio = 0.7)
trainC <- subset (satpred, splC == TRUE)
testC<- subset (satpred, splC == FALSE)

CapeCART <- rpart(Cape ~ ., data=trainC[, -c(4,5,7,8)], method= "class")

prp (CapeCART)
printcp(CapeCART)
plotcp(CapeCART)


predC <- predict (CapeCART, newdata = testC)
pred.probC <- predC[,2]
table(testC$Cape, pred.probC >=0.2)



#######################################
######### Vandenberg 

set.seed (123)
splV<- sample.split (satpred$Vandenberg , SplitRatio = 0.7)

trainV <- subset (satpred, splV == TRUE)
trainV <- trainV[, -c(4:6, 8)]
testV<- subset (satpred, splV == FALSE)
testV <- testV[, -c(4:6, 8)]

VandenbergCART <- rpart(Vandenberg ~ ., data=trainV, method= "class")
prp (VandenbergCART)
printcp(VandenbergCART)
plotcp(VandenbergCART)

predV <- predict (VandenbergCART , newdata = testV)
pred.probV <- predV[,2]
table(testV$Vandenberg, pred.probV >=0.16)

############################################

splX<- sample.split (satpred$Xichang , SplitRatio = 0.7)
trainX <- subset (satpred, splX == TRUE)
trainX <- trainX[, -c(4:7)]
testX<- subset (satpred, splX == FALSE)
testX <- testX[, -c(4:7)]

XichangCART <- rpart(Xichang ~ ., data=trainX, method= "class")
prp (XichangCART)

predX <- predict (XichangCART , newdata = testX)
pred.probX <- predX[,2]
table(testX$Xichang, pred.probX >=0.5)

```


