---
title: "Satellites"
author: "Frederic TWAHIRWA"
date: "11 février 2017"
output: html_document
---

```{r}

rm(list=ls(all=TRUE))

```

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(data.table)
library(ggplot2)
library(rworldmap)
library(ggmap)
library(geosphere)
library(RColorBrewer) 
library(forecast)
```
Data cleaning 
The data set required some transformations. 
- rename columns 
- remove strings in numerical columns 
- mutate news columns to keep informations removed in numerical culumns such as "end of life"" or "biginning of life""
- NR country as country of UN registry is replaced by the country owner name


```{r}

satellites<-fread(file='Database.csv', na.strings=c("", "NA"))

#rename columns
colnames(satellites)<-c("name_of_sat", "country_of_UN_registry", "owner", "country_of_owner", "users", "purpose",
                        "setailed_of_purpose", "class_of_orbit", "type_of_orbit", "long_of_geo_orbit", "perigee", 
                        "apogee", "eccentricity", "incrination", "period", "launch_mass", "dry_mass", "power",
                        "date_of_launch", "expected_lifetime", "contractor", "country_of_contractor","launch_site",
                        "launch_vehicule", "COSPAR_number", "NORAD_number")

# get class of each column
#lapply(satellites, class)

satellites$launch_mass<- as.numeric(satellites$launch_mass)
satellites$expected_lifetime<- as.numeric(satellites$expected_lifetime)
# Add a column End of Life (EOL)
satellites<- satellites %>% 
        mutate (end_of_life= as.numeric( grepl(pattern=".*EOL.*", satellites$power)))
satellites$end_of_life <- as.numeric(satellites$end_of_life | grepl(pattern=".*EOL.*", satellites$dry_mass))

# Add a column biginning  of Life (BOL)
satellites<- satellites %>% 
        mutate (biginning_of_life= as.numeric( grepl(pattern=".*BOL.*", satellites$power)))
satellites$biginning_of_life <- as.numeric(satellites$biginning_of_life | grepl(pattern=".*BOL.*", satellites$dry_mass))

#grep only numeric numbers in columns : power, expected_life_time 
satellites$power<-as.numeric(gsub("([0-9]+).*$", "\\1", satellites$power))
#satellites$expected_lifetime<-as.numeric(gsub("[^\\d]+", "",satellites$expected_lifetime, perl=T ))
satellites$dry_mass<-as.numeric(gsub("([0-9]+).*$", "\\1", satellites$dry_mass))


#Interpret Date of Launch column as date and extract year of launch....
satellites$date_of_launch <- as.Date(satellites$date_of_launch, "%m/%d/%Y")
satellites$year_of_launch <- as.integer(format(satellites$date_of_launch, "%Y"))
satellites$month_of_launch <- as.numeric(format(satellites$date_of_launch, "%m"))
satellites$day_of_launch <- as.numeric(format(satellites$date_of_launch, "%d"))
satellites$weekday_of_launch <- weekdays(satellites$date_of_launch)

# the system (function weekday) return the days of the week in French , I convert them manally in English
satellites$weekday_of_launch<-gsub("lundi","1_Monday", satellites$weekday_of_launch)
satellites$weekday_of_launch<-gsub("mardi","2_Tuesday", satellites$weekday_of_launch)
satellites$weekday_of_launch<-gsub("mercredi","3_Wednesday", satellites$weekday_of_launch)
satellites$weekday_of_launch<-gsub("jeudi","4_Thursday", satellites$weekday_of_launch)
satellites$weekday_of_launch<-gsub("vendredi","5_Friday", satellites$weekday_of_launch)
satellites$weekday_of_launch<-gsub("samedi","6_Saturday", satellites$weekday_of_launch)
satellites$weekday_of_launch<-gsub("dimanche","7_Sunday", satellites$weekday_of_launch)

```

Exploring data 
 - recency : based on the dataset 438 satellites exceed their expected life time
 - activitities by days and months :  the finding is that there are far few satellites launched in January while the peack of activity lies on Thusday  (by day) and in June (by month)

```{r}

# add a new column to highliht the satellite recency  and verify if there are satellites which ecxeeds their expected life delay 
# 438 sateliites exceed their expeted life delay
satellites$years_since <- as.numeric(2017- satellites$year_of_launch) 
satellites$exceed_expected_life <-as.numeric (satellites$years_since > satellites$expected_lifetime)
n_sat_exceed_expected_life <- sum (satellites$exceed_expected_life, na.rm=TRUE)

#replace NR by noum of owner country
satellites$country_of_UN_registry[which(satellites$country_of_UN_registry=="NR")]<-
        satellites$country_of_owner[satellites$country_of_UN_registry=="NR"]

theme1 <- theme (plot.title = element_text(color="blue", size=14, hjust =0.5, face="bold.italic"),
             axis.title.x = element_text(color="blue", size=12, face="bold"),
             axis.title.y = element_text(color="blue", size=12, face="bold"))

ggplot(satellites, aes(weekday_of_launch, fill=factor(month_of_launch))) +
        geom_bar() + 
        ggtitle( "satellites launched by weekday and month") +
        labs(x="The weekday of launch", y="Number of satellites") +  
        theme1

ggplot(satellites, aes(weekday_of_launch, fill=factor(month_of_launch))) +
        geom_bar(position="dodge") +
        ggtitle( "satellites launched by weekday and month") +
        labs(x ="Country of UN registry",y ="Number of satellites") +
        theme1

ggplot(satellites, aes(month_of_launch, fill=factor(weekday_of_launch))) + 
        geom_bar(position="dodge") + 
        ggtitle( "satellites launched by weekday") +
        labs(x ="Country of UN registry", y ="Number of satellites") +
        theme1


number_by_wday_of_launch<-satellites %>% 
        group_by(weekday_of_launch) %>% 
        summarise(number_by_weekday=n()) %>% 
        arrange(desc(number_by_weekday))

number_by_month_of_launch<-satellites %>% 
        group_by(month_of_launch) %>% 
        summarise(number_by_month=n()) %>% 
        arrange(desc(number_by_month))

number_by_year_of_launch<-satellites %>% 
        group_by(year_of_launch) %>% 
        summarise(number_by_year=n()) %>% 
        arrange(desc(year_of_launch))

ggplot(number_by_year_of_launch, aes(x=year_of_launch, y=number_by_year,
                                     size=number_by_year, col=number_by_year))+
        geom_point(alpha=0.8)+
        geom_smooth(se=F, linetype = 2)+
        ggtitle( "actives satellites in orbit up to 2016") + 
        labs( x="launch year", y="Number launched by year") +
        theme1
        

ggplot(satellites, aes(x=1, y=apogee, col=factor(class_of_orbit))) +
        geom_point(alpha=.5, position=position_jitter(width=1)) 

```

EXPLORING DATA SEGMENTATION 
 - number of active satellites by country

 
 Findings : 
 - 38.4% of satellites are under the sole USA Flag
 - Chine is in second position, and trying to catch up in the area of satellites in orbit
 - 7 countries have at least 40 actives satellites on orbit
 - 23 satellites are at least under the flg of two countries

```{r}
origin_country<- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        arrange(desc(sat_number_from_orig_country)) %>% 
        mutate (percent=round(100*sat_number_from_orig_country / sum (sat_number_from_orig_country),1))

share_sat<- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        filter(grepl("/", country_of_UN_registry)) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        arrange(desc(sat_number_from_orig_country)) %>% 
        mutate (percent=round(100*sat_number_from_orig_country / sum (sat_number_from_orig_country),1))

n_of_shared_sat <- sum (share_sat$sat_number_from_orig_country)

# countries that have few satellites in orbit less than 40 
country_low_power <- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        filter (sat_number_from_orig_country < 40) %>%  # the threshold is set @ 40 satellites 
        arrange(desc(sat_number_from_orig_country))

n_low_power_countries <- sum (country_low_power$sat_number_from_orig_country)

# countries that have more 40 satellites in orbit 
country_high_power <- satellites %>% 
        group_by(country_of_UN_registry) %>% 
        summarise(sat_number_from_orig_country=n()) %>% 
        filter (sat_number_from_orig_country >= 40) %>% 
        arrange(-sat_number_from_orig_country) %>% 
        rbind (c("Others countries ", n_low_power_countries))


# visualizing the share umbalance and the USA power
share_sat_plot <- ggplot(country_high_power,
                         aes(x=reorder(country_of_UN_registry, -as.numeric(sat_number_from_orig_country)),
                                                 y = as.numeric(sat_number_from_orig_country))) +                          geom_bar(stat="identity", fill="steelblue") + 
        geom_text(aes(label=sat_number_from_orig_country), vjust=1.5, color="white", size=4) + 
        ggtitle( "Satellites distribution by county") +
        scale_x_discrete(name ="Country of UN registry") +  # rename x axis
        scale_y_discrete(name ="Number of satellites") + # rename y axis
        theme_minimal() 
       

share_sat_plot

US_vs_chine <- satellites %>% 
        group_by(country_of_UN_registry, year_of_launch) %>% 
        filter((country_of_UN_registry=="USA" | country_of_UN_registry=="China" |
                        country_of_UN_registry=="France") & (year_of_launch < 2016 & year_of_launch > 1996)) %>%
        summarise(sat_number_from_orig_country=n()) %>% 
        arrange(desc(year_of_launch))

# visualizing USA power compared to China and France on the past years 
ggplot(US_vs_chine, aes(x=year_of_launch, y=sat_number_from_orig_country,
                        group = country_of_UN_registry, colour = country_of_UN_registry)) +
        geom_line() +
        geom_point( size=4, shape=21, fill="white")

# visualizing USA power compared to China and France on the past years  with bar plot
ggplot(US_vs_chine, aes(x=year_of_launch, y=sat_number_from_orig_country,
                        fill=factor(country_of_UN_registry))) +
        geom_bar(stat = "identity", position="dodge")

# The world distribution 
# the world map
names(origin_country)<- c("region", "sat_number_from_orig_country")

all_states <- map_data("world")
world_sat <-inner_join(all_states, origin_country, by="region")

#plot all states with ggplot

world_base <- ggplot(data = all_states, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.5) + 
  geom_polygon(color = "white", fill = "gray")


World_n_sat<-world_base +
        geom_polygon(data = world_sat, aes(fill = sat_number_from_orig_country), color = "white")+
        #scale_fill_continuous(name = "number satellite per Country")+ 
        scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(10, 50, 100, 200, 300, 400),
                         trans = "log10")+
        ggtitle( "Satellites distribution by county \b at golbal level")
        theme_bw()
       
World_n_sat
```

EXPLORING DATA SEGMENTATION 
 - number of active satellites by launch site
 
 Findings : 
 - 38.4% of satellites are under the sole USA Flag
 - Chine is in second position
 - 7 countries have at least 40 actives satellites on orbit
 - 23 satellites are at least under the flg of two countries


```{r}
site_of_launch <-satellites %>% 
        group_by (launch_site) %>%
        summarise(sat_number_by_site=n(), total_mass= sum(launch_mass, na.rm=TRUE),
                  min_mass= min (launch_mass, na.rm=TRUE),
                  max_mass = max (launch_mass, na.rm=TRUE), mean_mass = mean(launch_mass, na.rm=TRUE),
                  sd_mass = sd(launch_mass, na.rm = TRUE))  %>%
        top_n(10, sat_number_by_site) %>% 
        arrange (desc (sat_number_by_site)) %>% 
        mutate(percentage = round(100*sat_number_by_site / sum(sat_number_by_site),1)) %>% 
        mutate(pos=cumsum(sat_number_by_site)-sat_number_by_site /2)

# visualizing where satellites are launched by site        
bp_site = ggplot(site_of_launch, aes(x= reorder(launch_site, -as.numeric(sat_number_by_site)),
                                     y = sat_number_by_site, fill = factor(launch_site)))+
        geom_bar(stat="identity") +  #??? aggregate data into accounts 
        theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5)) + # vertical label
        geom_text(aes(label=sat_number_by_site), vjust=1.5, color="white", size=4) + 
        ggtitle( "Where active satellites are launched") + 
        scale_x_discrete(name ="Site") + 
        scale_y_discrete(name ="Number of satellites") 
bp_site

bp_site_mass = ggplot(site_of_launch, aes(x= reorder(launch_site, as.numeric(total_mass)),
                                     y = total_mass, fill = factor(launch_site)))+
        geom_bar(stat="identity") + 
        coord_flip() +
        geom_text(aes(label=total_mass), vjust=-4.0, color="black", size=3) + 
        ggtitle( "total mass in orbit by site ") + 
        scale_x_discrete(name ="Site") + 
        scale_y_discrete(name ="Mass total") 
bp_site_mass

veh_of_launch <-satellites %>% 
        group_by (launch_site, launch_vehicule) %>% 
        summarize (sat_by_veh= n()) %>% 
        arrange (desc (sat_by_veh))
```

- Exploring data 
 - display number of satellites given their expected life and highlight their distribution based on their users and class of orbit
 - This information can help in dealing with missing value
 - 39 % of actives satellites : Commercials
 - 20 % of actives satellites : governments
 - 39 % of actives satellites : Military
 - 49 % 
Distribution by class 
 - Since the 2000s, the number of Elliptical, MEO and GEO satellites launched haven't changed while the number of LEO have significantly increased from 35 in 2010 to 119 in 2015
 

```{r}

# visualization of satellites expected liftime by sector
ggplot(satellites, aes(x=expected_lifetime, fill=users)) +
        geom_histogram(binwidth=1, alpha=.5, position="identity")+
        ggtitle( "distribution: Satellites expected lifetime by sector") + 
        labs( x="expected lifetime", y="satellites number") +
        theme1

# visualization of satellites by class of orbit
ggplot(satellites, aes(x=expected_lifetime, fill=class_of_orbit)) + 
        geom_histogram(binwidth=1, alpha=.5, position="identity") +
        ggtitle( "distribution : Satellites by class of orbit") + 
        labs( x="expected lifetime", y="satellites number") +
        theme1

# distribution of satellites in orbit  by sector and purpose
sat_users <- satellites %>% 
        group_by (users) %>%
        summarise (sat_number_by_users=n(), min_exepect_life = round(min (expected_lifetime, na.rm=TRUE),1),
                  max_expect_life = round(max (expected_lifetime, na.rm=TRUE),1),
                  mean_expect_life = round(mean(expected_lifetime, na.rm=TRUE),1),
                  sd_expect_life = round(sd(expected_lifetime, na.rm = TRUE),1))  %>%
        mutate (percent=round(100*sat_number_by_users / sum (sat_number_by_users),0)) %>% 
        arrange (desc (sat_number_by_users))

sat_purpose <- satellites %>% 
        group_by (purpose) %>%
        summarise (sat_number_by_purpose=n())  %>%
        mutate (percent = round(100*sat_number_by_purpose / sum (sat_number_by_purpose),0)) %>% 
        arrange (desc (sat_number_by_purpose))

sat_users1 <- satellites %>% 
        group_by (users, purpose) %>% 
        summarise (sat_number_by_userp = n()) %>%
        arrange (desc (sat_number_by_userp)) 
        #mutate (percent = round(100*sat_number_by_userp / sum (sat_number_by_userp),0))

        

sat_class <- satellites %>% 
        group_by (class_of_orbit) %>%
        summarise (number_by_class=n(), min_exepect_life = round(min (expected_lifetime, na.rm=TRUE),1),
                  max_expect_life = round(max (expected_lifetime, na.rm=TRUE),1),
                  mean_expect_life = round(mean(expected_lifetime, na.rm=TRUE),1),
                  sd_expect_life = round(sd(expected_lifetime, na.rm = TRUE),1))  %>%
        mutate (percent = round (100*number_by_class / sum (number_by_class) )) %>% 
        arrange (desc (number_by_class))

# visualization of satellites by class of orbit
ggplot(sat_class, aes(x=class_of_orbit, y=number_by_class, fill=factor(class_of_orbit))) + 
        geom_bar(stat = "identity", position="dodge") + 
        ggtitle( "Satellites number  by class of orbit") + 
        labs( x="class of orbit", y="satellites number") +
        theme1

sat_class_ts <- satellites %>% 
        group_by (class_of_orbit, year_of_launch) %>%
        filter (!is.na(class_of_orbit) & year_of_launch < 2016 & year_of_launch > 1998) %>% 
        summarise (number_by_class=n())  %>%
        # mutate (percent = round (100*number_by_class / sum (number_by_class) )) %>% 
        arrange (desc (year_of_launch))

# visualization of satellites by class of orbit and year of launch
ggplot(sat_class_ts, aes(x=year_of_launch, y=number_by_class, fill=factor(class_of_orbit))) + 
        geom_bar(stat = "identity", position="dodge") + 
        ggtitle( "Satellites number by launch year and class of orbit") + 
        labs( x="launch year", y="sat number by class of orbit") +
        theme1

ggplot(sat_class_ts, aes(x=year_of_launch, y=number_by_class,
                        group = class_of_orbit, colour = class_of_orbit)) + 
        geom_line(size=1.5) + 
        geom_point( size=4, shape=21, fill="white")+
        ggtitle( "Satellites number by launch year and class of orbit") + 
        labs( x="launch year", y="sat number by class of orbit") +
        theme1

```


Owner and purpose

```{r}
sat_Owner<- satellites %>% 
        group_by (owner, country_of_owner) %>% 
        summarise (number_by_owner=n())  %>% 
        arrange (desc (number_by_owner))

sat_Owner_purpose <- satellites %>% 
        group_by (owner,country_of_owner, users) %>% 
        summarise (number_by_owner_purpose=n())  %>% 
        arrange (desc (number_by_owner_purpose))


```



```{r}
sat_mass<-satellites %>% 
        select (launch_mass) %>% 
        filter (!is.na(launch_mass))

sat_mass_clust<- hclust (d = dist(sat_mass$launch_mass))
plot (sat_mass_clust)

##############################
sat_expected_life <- satellites %>% 
        filter (!is.na(expected_lifetime))
sat_exlife_clust<- hclust (d = dist(sat_expected_life$expected_lifetime))
plot (sat_exlife_clust)


hist(sat_expected_life$expected_lifetime)

linreg_users=lm(expected_lifetime~users,data=sat_expected_life)
cor(linreg_users$fitted.values,sat_expected_life$expected_lifetime)
plot(sat_expected_life$expected_lifetime,linreg_users$fitted.values)
hist(linreg_users$fitted.values)

linreg_class=lm(expected_lifetime~class_of_orbit,data=sat_expected_life)
cor(linreg_class$fitted.values,sat_expected_life$expected_lifetime)
plot(sat_expected_life$expected_lifetime,linreg_class$fitted.values)
hist(linreg_class$fitted.values)

summary(linreg_users)
summary(linreg_class)

```

```{r}
# cov (sat_expected_life$expected_lifetime,sat_expected_life$users)

```



Time series
- try to forecast number of satellites launched in 2016 given satellites (actives) in orbit launched in 11 previous years
- 

```{r}

sat_by_year <- satellites %>% 
        group_by(year_of_launch) %>% 
        filter ( year_of_launch>=2005 & year_of_launch < 2016) %>% 
        summarise (n_by_month=n())



timeseries_sat <- ts (sat_by_year[,2], start=2005, end=2015)
ts.plot (timeseries_sat)

#autocolrrelation 
acf(timeseries_sat, plot=FALSE) # acf [1]= 0.653 acf [2]= 0.351
n_sat_change <- diff (timeseries_sat)

#autoreggressive 
AR_sat<- arima (timeseries_sat, order=c(1,0,0)) 
print (AR_sat) # slope :1 , intercept: 252.3669, variance : 278.8

AR_sat_change <- arima (n_sat_change, order=c(1,0,0))

ts.plot(timeseries_sat)
AR_sat_fitted <- timeseries_sat- residuals(AR_sat)
points(AR_sat_fitted, type = "l", col = 2, lty = 2)

predict_AR_sat <-predict(AR_sat_fitted, 1) # 149

# Moving average
n_sat_change <- diff (timeseries_sat)

ts.plot(n_sat_change)
MA_sat_change <-arima (n_sat_change, order=c(0,0,1)) # slope =0.8349 , intercept=90.88, variance : 771
MA_sat_change_fitted <- n_sat_change - residuals(MA_sat_change)

points(MA_sat_change_fitted, type = "l", col = 2, lty = 2)
predict_MA_sat <-predict(MA_sat_change, 1)
print (predict_MA_sat)

MA_sat <-arima (timeseries_sat, order=c(0,0,1)) # slope =0.8349 , intercept=90.88, variance : 771
ts.plot(timeseries_sat)
MA_sat_fitted <- timeseries_sat - residuals(MA_sat)
points(MA_sat_fitted, type = "l", col = 2, lty = 2)

predict_MA_sat1 <-predict(MA_sat_fitted, 1) #110.9
print (predict_MA_sat1)

# comparison between AR and MA

AIC(AR_sat_change) # 81.98
AIC(MA_sat_change) # 82.04

BIC(AR_sat_change) # 82.89
BIC(MA_sat_change) # 82.95
##########################################################

auto_a_sat <- auto.arima(timeseries_sat)
auto_a_sat

```



Time series
- try to forecast number of satellites launched in 2016 given satellites (actives) in orbit launched in 5 previous years


```{r}
sat_by_year <- satellites %>% 
        group_by(year_of_launch) %>% 
        filter ( year_of_launch>=2010 & year_of_launch < 2016) %>% 
        summarise (n_by_year=n())

timeseries_sat <- ts (sat_by_year[,2], start=2010, end=2015)
plot(timeseries_sat)

#autocolrrelation 
acf(timeseries_sat, plot=FALSE) # acf [1]= 0.491 acf [2]= 0.055
n_sat_change <- diff (timeseries_sat)

#autoreggressive 
AR_sat<- arima (timeseries_sat, order=c(1,0,0)) 
print (AR_sat) # slope : 0.846 , intercept: 121.023, variance : 517.2

AR_sat_change <- arima (n_sat_change, order=c(1,0,0))

ts.plot(timeseries_sat)
AR_sat_fitted <- timeseries_sat- residuals(AR_sat)
points(AR_sat_fitted, type = "l", col = 2, lty = 2)

predict_AR_sat <-predict(AR_sat_fitted, 1) # 145.5

# Moving average
n_sat_change <- diff (timeseries_sat)

ts.plot(n_sat_change)
MA_sat_change <-arima (n_sat_change, order=c(0,0,1)) # slope =-0.9998 , intercept=20.14, variance : 91.45
MA_sat_change_fitted <- n_sat_change - residuals(MA_sat_change)

points(MA_sat_change_fitted, type = "l", col = 2, lty = 2)
predict_MA_sat <-predict(MA_sat_change, 1)
print (predict_MA_sat) #13.99 

MA_sat <-arima (timeseries_sat, order=c(0,0,1)) # slope =0.68 , intercept= 117.9, variance : 747
ts.plot(timeseries_sat)
MA_sat_fitted <- timeseries_sat - residuals(MA_sat)
points(MA_sat_fitted, type = "l", col = 2, lty = 2)

predict_MA_sat1 <-predict(MA_sat_fitted, 1) #113.58
print (predict_MA_sat1)

# comparison between AR and MA

AIC(AR_sat_change) # 45.07
AIC(MA_sat_change) # 44.55

BIC(AR_sat_change) # 43.09
BIC(MA_sat_change) # 82.38

# using auto.arim model 

```

```{r}
sat_by_month <- satellites %>% 
        group_by(year_of_launch, month_of_launch) %>% 
        filter ( year_of_launch>=2005 & year_of_launch < 2016) %>% 
        summarise (n_by_month=n()) %>% 
        arrange (year_of_launch)

# Here we can realize that some months lacking , so to I complete the data.frame by adding those months with zero as value of number of sat
# this help on computing time series anaysis 

y<- c(2006, 2009)
m <- c(1,3)
v <- c(0,0)
addrows<- data.table("year_of_launch"=y, "month_of_launch"=m,"n_by_month"=v)

sat_by_month <- rbind(as.data.frame(sat_by_month), as.data.frame(addrows)) # why I had to coerce  sat_by_month and addrow<s              
sat_by_month <-arrange (sat_by_month,year_of_launch, month_of_launch)

ts_sat <- ts (sat_by_month[,3], start=c(2005, 1), end=2015, frequency = 12)
ts_sat
plot (ts_sat)

auto_a_sat <- auto.arima(ts_sat)
auto_a_sat

theforecast <-forecast(object=auto_a_sat, h = 12)
summary(theforecast)
plot (theforecast) 

## â•â•â•â•â•â•â•â•â•â•â•â•â•â•
## the resultf of the forecasting, how to intrepret them 
## There is a simple way to plot the forecast graph with ggplot ?
## â•â•â•â•â•â•â•â•â•â•â•â•â•â•

```